Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-07-31 Thesis/chapter/03-theoretical-background.tex
ANOVA

DOEs: randomization, latin square
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Linear Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AI vs statistics}
\begin{itemize}
	\item \td{let GPT-3 write}
	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
	\item 
		\href
		{https://doi.org/10.1177\%2F1352458520978648}
		{Machine and deep learning in MS research are just powerful statistics – No}
\end{itemize}

>>>>

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Analysis of Variance} % ANOVA
The statistical significance of the experiment is determined by a ratio of two variances. This ratio is independent of several possible alterations to the experimental observations: Adding a constant to all observations does not alter significance. Multiplying all observations by a constant does not alter significance. 
So ANOVA statistical significance result is independent of constant bias and scaling errors as well as the units used in expressing observations. %https://en.wikipedia.org/wiki/Analysis_of_variance#Summary_of_assumptions
\td{make analysis with EMMA dataset and EMMA+DOE}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Linear Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AI vs statistics}
\begin{itemize}
	\item \td{let GPT-3 write}
	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
	\item 
		\href
		{https://doi.org/10.1177\%2F1352458520978648}
		{Machine and deep learning in MS research are just powerful statistics – No}
\end{itemize}
